---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Problem 2 

We will be creating interactive plots in plotly.

```{r, message = FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

We will use the `ny_noaa` dataset from the `p8105.datasets` package. This dataset includes weather data/summary statistics from weather stations around the world. Each observation holds information (e.g., variables included are `id`, `date`, `prcp`, `snow`, `snwd`, `tmax`, `tmin`) from a single weather station. 

```{r}
data("ny_noaa")
```

We will do some initial data cleaning/subsetting. 

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = case_match(
      id, 
      "USW00094728" ~ "CentralPark_NY", 
      "USW00022534" ~ "Molokai_HI",
      "USS0023B17S" ~ "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

Let's create some plots! First, I will be creating a scatterplot, showing the relationship between `tmax` (maximum temperature (tenths of degrees C)) and `tmin` (minimum temperature (tenths of degrees C)). 

```{r}
weather_df |>
  mutate(text_label = str_c("Name: ", name)) |>
  plot_ly(
    x = ~tmax, y = ~tmin, color = ~name,
    type = "scatter", mode = "markers"
  )
```

Next, I will be creating a boxplot. 

```{r}
weather_df |>
  mutate(name = fct_reorder(name,tmin)) |>
  plot_ly(
    x = ~ name, y = ~prcp,
    type = "box", colors = "viridis")
```

Lastly, I will be creating a bar chart with the number of the weather stations observations for the 3 included (NY, HI, WA) in the cleaned `ny_noaa` dataset. 

```{r}
weather_df |>
  count(name) |> 
  mutate(neighbourhood = fct_reorder(name, n)) |> 
  plot_ly(
    x = ~name, y = ~n, 
    type = "bar")
```

